Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2021-11-27 papers/01 Reply round 1/response_TSG.tex

%%%%%%%%%%%%%%%%%%%%%%%%%
% Response to reviewer Template
% C. Ocampo-Martinez (2014)
%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper,left=3.0cm,right=3.0cm,top=2.0cm,bottom=2.0cm]{geometry}
\setlength{\parskip}{2ex}
\setlength{\parindent}{0ex}

\usepackage[english]{babel}
\usepackage{times, epsfig, subfigure, psfrag, amssymb, amsmath, amsbsy, amsfonts}
\usepackage{graphics}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{url,soul,ulem}
\usepackage{stfloats}
\usepackage{array, color}
\usepackage{bm}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{datetime,enumitem}
\usepackage{algorithmic}
\usepackage{cite}
\usepackage[dvipsnames]{xcolor}
\usepackage{algorithm}
\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{empheq}
\setlist[enumerate]{label=\alph*),topsep=0ex,parsep=0ex,partopsep=0ex}

\newtheorem{definition}{Definition}%{\itshape}{\bfseries}
\newtheorem{example}{Example}%{\it}{}
\newtheorem{corollary}{Corollary}%{\it}{}
\newtheorem{proposition}{Proposition}%{\it}{}
\newtheorem{lemma}{Lemma}%{\it}{}
\newtheorem{theorem}{Theorem}%{\it}{}
\newtheorem{remark}{Remark}%{\it}{}
\newtheorem{assumption}{Assumption}%{\it}{}
%\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
%\newcommand{\proof}{\vspace{1mm}\noindent{\it Proof.}\quad}
%\def\qed{\quad{$\square$}}

%\textwidth=6.3in
%\textheight 9in 
%\setlength{\topmargin}{-0.5in}
%\setlength{\oddsidemargin}{0.1in} 
%\setlength{\evensidemargin}{0.1in}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\an#1{{{\bf \color{blue}#1}}}
\def\o{{\bm{\omega}}}
\def\vmean{v^{\rm mean}}
\def\vmax{v^{\rm max}}	
\def\e{\epsilon}
\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \marginpar{\textsc{ToDo}}
	\framebox{\begin{minipage}[c]{0.9 \textwidth} \tt #1
	\end{minipage}}\vspace{5 mm}\par}

% Boldsymbols, mathcal, mathbb
\newcommand{\bs}{\boldsymbol}
\newcommand{\mc}{\mathcal}
\newcommand{\bb}{\mathbb}
\newcommand{\R}{\bb R}

\DeclareMathAlphabet{\mathbbmsl}{U}{bbm}{m}{sl}
\newcommand{\bbi}{\mathbbmsl}
%norm
\newcommand{\norm}[1]{\left\|#1\right\|}

% Operators and notations
\newcommand{\dom}{\operatorname{dom}}
\newcommand{\iP}{\mathcal{P}}
\newcommand{\B}{\mathcal{C}}
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\argmin}{\operatorname{argmin}}
\newcommand{\mini}{\operatorname{minimize}}
\newcommand{\Proj}{\mathrm{Proj}}
\newcommand{\fix}{\mathrm{fix}}
\newcommand{\proj}{\mathrm{proj}}
\newcommand{\prox}{\mathrm{prox}}
\newcommand{\Id}{\mathrm{Id}}
\newcommand{\Res}{\operatorname{J}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\blkdiag}{\operatorname{blkdiag}}
\newcommand{\col}{\operatorname{col}}
\newcommand{\zer}{\operatorname{zer}}
\newcommand{\nulls}{\operatorname{Null}}
\newcommand{\range}{\operatorname{Range}}
\newcommand{\dist}{\mathrm{dist}}
\newcommand{\nc}{\mathrm{N}}
\newcommand{\0}{\mathbf{0}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\half}{^1\hspace*{-.1em}/_2}
\newcommand{\gph}{\operatorname{gph}}
%Roman numbers
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\newcommand{\eod}{\ensuremath{\hfill\Box}}
\newcommand{\qedd}{\ensuremath{\hfill \blacksquare}}

% Add time and date to pages
% *****************************************
%\cfoot[\thepage]{\thepage}
%\chead[]{}\lhead[\currenttime]{\currenttime}\rhead[\today]{\today}
%\pagestyle{fancy}
% *****************************************
\usepackage[nobottomtitles*]{titlesec}
\titleformat{\section}%
    {\bfseries\large}{}{0.0em}{}[]%
\titlespacing*{\section}%
    {-0.5cm}{2.5ex plus 0.2ex minus 0.2ex}{0.5ex plus 0.2ex minus 0.2ex}%

\usepackage{ifthen}
\newcommand{\query}[2][]{
    \ifthenelse{\equal{#1}{}}{}{\textbf{#1:}~}\emph{#2}\\[0.1em]}
\newcommand{\ans}[1]{\textbf{Answer:~}
    \ifthenelse{\equal{#1}{}}{To be answered!}{#1}}

% Use for adding comments according to the author (different color)
% CUSTOMIZE
%\newcommand{\XXX}[1]{\textcolor{red}{#1}}
\newcommand{\com}[1]{\textcolor{blue}{#1}}
\newcommand{\edit}[1]{\color{blue}{#1 }\color{black} }
\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
%\newcommand{\XX}[1]{\textcolor[rgb]{0,0.5,0}{#1}}
%\newcommand{\XXXX}[1]{\textcolor[rgb]{0.50,0.00,0.50}{#1}}

\title{Authors' response}
\date{}
\begin{document}
%\maketitle

\begin{center}
\textbf{\Large Authors' response}
\end{center}
\vspace{0.5cm}
\noindent

\textbf{Ms. Ref. No.: TSG-01404-2021}  \\
\textbf{Title: Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism}   \\
\textbf{Authors: G. Belgioioso, W. Ananduta, S. Grammatico, and C. Ocampo-Martinez}   \\
\textbf{Journal: IEEE Transactions on Smart Grid}

%\vspace{1cm}

\setcounter{page}{1}

% ADD HERE PREAMBLE TEXT
The authors would like to thank the Reviewers and the Associate Editor for their comments, which have helped us to improve the manuscript. We do hope that all the points raised have been addressed. {To help reviewing the revised manuscript,} the points have been divided up and marked AE, R1, R2, R3, and R4, for comments from Associate Editor, Reviewers 1, 2, 3, and 4, respectively. When appropriate, the corresponding marks can be found within the manuscript and the modifications according to the comments are highlighted in \textcolor{blue}{blue}. In addition, the cross references of equation labels, as mentioned by the reviewers and used in the answers, are adapted based on the revised manuscript. %We have also removed some intermediate steps in the derivation of some (in)-equalities and displayed some equations in different forms to meet the page limit. These parts are highlighted in \textcolor{magenta}{magenta}.%Additionally, in order to adjust the contents into a technical note, we have streamlined some parts of the paper, which are highlighted in \textcolor{magenta}{magenta}.

\section*{Answers to Associate Editor}

\query[AE-1]{This paper proposes a generalized Nash game model for P2P energy trading in a distribution network considering network constraints and DNO. A distributed algorithm is developed to seek the equilibrium of the game. The topic is relevant and timely. However, the reviewers raised some concerns. The authors should carefully consider all the comments and make a corresponding improvement. }

\ans{}

\newpage
\section*{Answers to Reviewer 1}

\query[R1-1]{This paper proposed a peer-to-peer energy market for prosumers as a generalized aggregative game. The paper is well written, and the research may be of value. The reviewer mainly concerns about the proposed algorithm.}
\ans{We thank the reviewer for the positive comment.}

\textit{The comments are as follows:}

\query[R1-2]{The feasibility of such scenarios still remains further discussions considering the capital costs of energy storage, interests conflicts of current electrical roles, and the engineering implementations involving such accurate models.}
\ans{We agree with the Reviewer. This work shows how peer-to-peer market scenarios in theory can be beneficial.}

\query[R1-3]{The charging and discharging efficiency are not considered in (5), which is sometimes acceptable, but requires explanations.  }
\ans{In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assume the simplest model of the storage since component model is not the main focus of this work. However, based on this reviewer comment, we now update the storage dynamics, which include the charging and discharging efficiencies. Therefore, for each storage unit, we consider two decision variables, i.e., the charging and discharging powers. The storage unit is now modeled as follows:}

\textit{``\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics}}
%
\begin{equation}
%	\marginnote{\note{R1-3}\\ \note{R2-2}}
	\begin{aligned}
		\left.
		\begin{array}{c}
			\edit{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
			\edit{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
		\end{array}
		\hspace{-5pt} \right\} & \begin{matrix}
			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
		\end{matrix} \\
		\edit{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
\textit{where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, \edit{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p}^{\mathrm{ch}}_i \geq 0$ and $\edit{\overline p}^{\mathrm{ds}}_i \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.''}

We have also modified our game formulation and proposed algorithm in Section III to take into account this storage model update.

\query[R1-4]{The energy loss of the distribution network is also not considered.}
\ans{We do not include energy loss of the distribution network in the current setup and leave it for future work. In this manuscript, we focus on the game-theoretic formulation of the interaction among prosumers and the network operator.}

\query[R1-5]{The individual variables, coupled relationships for these energy roles, and the corresponding dual variables should be explained specifically, along with the whole framework structure for equilibrium. The rationalities of the framework is not clear. At least, the current presentation is hard to follow.  }
\ans{}

\query[R1-6]{The P2P trading prices are given parameters, which are quite unreasonable. In fact, the P2P prices are the key variable in most literature.}
\ans{\comment{Wicak}\comment{provide some references that consider this. Check dual variable as marginal price.}}

 \query[R1-7]{The algorithm requires too many iterations, which leads to poor feasibility in real applications, especially in distributed environment. }
 \ans{\comment{for day-ahead or intra-day markets (with sufficiently large sampling time), our numerical experience shows the algorithm is tractable.}}

\newpage
\section*{Answers to Reviewer 2}

\query[R2-1]{This manuscript proposes a game model for P2P energy trading in a distribution network considering network constraints and the DNO agent. The game model is a generalized game in which agents have coupled objectives and constraints. A distributed algorithm is developed to seek the equilibrium of the game. The topic of this manuscript is interesting, and the presentation is clear in general. The reviewer has some comments on the model and algorithm. }
\ans{We thank the Reviewer for the positive comment.}

\query[R2-2]{In common energy storage models, efficiency is usually a coefficient of the charging/discharging power. The storage model in (5) is uncommon as the authors take the efficiency $a_i$ as a coefficient of energy state $x_{ih}$. In related works (such as (6) in https://ieeexplore.ieee.org/document/8919970), the coefficient of energy states is usually called a leakage coefficient, describing energy leakage over time. References may be needed for (5), and please explain in what sense this storage model (5) is practical.  }
\ans{We thank the reviewer for raising this point and suggesting the reference. In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assume the simplest model of the storage since component model is not the main focus of this work. However, based on this reviewer comment, we now update the storage dynamics, which include the charging and discharging efficiencies. Therefore, for each storage unit, we consider two decision variables, i.e., the charging and discharging powers. The storage unit is now modeled as follows:}

\textit{``\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics}}
%
\begin{equation}
	%	\marginnote{\note{R1-3}\\ \note{R2-2}}
	\begin{aligned}
		\left.
		\begin{array}{c}
			\edit{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
			\edit{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
		\end{array}
		\hspace{-5pt} \right\} & \begin{matrix}
			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
		\end{matrix} \\
		\edit{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
\textit{where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
	%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
	, \edit{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
	$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p}^{\mathrm{ch}}_i \geq 0$ and $\edit{\overline p}^{\mathrm{ds}}_i \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.''}

We have also modified our game formulation and proposed algorithm in Section III to take into account this storage model update.

### 2021-12-07 papers/02 journal v2/journal_v14.tex
update docs
update manuscript and reply letter

\smallskip
We consider a linear approximation of power-flow equations, which is standard in the literature of P2P markets, e.g., \cite{yang2019,moret2020}. Specifically, for each bus $y \in \mc B$, it must hold that
\begin{equation}
\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \left(p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}\right)-p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
\end{equation}
which indicates local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption and line powers. Moreover, it must hold that
\begin{subequations}
\small
\label{eq:pf_pq}
\begin{align}
&p_{(y,z)}^{\ell} = B_{(y,z)}\left({\theta_y - \theta_z} \right) - G_{(y,z)}\left(v_y - v_z \right), \, \, \forall z \in \mc B_y, \label{eq:pf_p}\\
&q_{(y,z)}^{\ell} = G_{(y,z)}\left({\theta_y - \theta_z} \right) + B_{(y,z)}\left(v_y - v_z \right), \, \,  \forall z \in \mc B_y, \label{eq:pf_q}
\end{align}
\end{subequations}
which represent the power flow equations of line $(y,z)$ from the perspective of bus $y$, with $B_{(y,z)}$ and  $G_{(y,z)}$ denoting the susceptance and conductance, respectively, of line $(y,z)$. Note that by \eqref{eq:pf_p} and \eqref{eq:pf_q}, for each pair $(y,z) \in \mc L$, it holds that $p_{(y,z)}^{\ell} = {-p}_{(z,y)}^{\ell}$ and $q_{(y,z)}^{\ell} = {-q}_{(z,y)}^{\ell}$.

@@

\begin{remark}
Our definitions of $J_i$, $\mc U_i$ and $\mc C$ satisfy Assumption \ref{as:gen}. Moreover, these definitions can be expanded by incorporating additional cost terms, for example, related to the degradation of storage units and constraints (e.g. ramping constraints of dispatchable generation units), as long as Assumption \ref{as:gen} remains satisfied. \eod
\end{remark}

@@

\begin{algorithm*}[htbp]
\caption{Distributed P2P Markets Clearing Mechanism \red{[include charging and discharging]}}
\label{alg:alg1}
\begin{algorithmic}[1]
\small

\init{ }
\State
\textbf{Prosumers.} For all $i \in \mc N$: set $u_i(0) \in \mc U_i$, $\mu^{\text{tr}}_{(i,j)}(0) = \0$, $\forall j \in \mc N_i$; $\alpha_i \!<\! 
3 +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$.
\State
\textbf{DNO.} Set $u_{N+1}(0) \!\in\! \mc U_{N+1}$, $\lambda^{\text{mg}}\!=\!\0$, $\mu^{\text{tg}} \!=\! \0$, $\mu_y^{\text{pb}}(0)\! = \!\0$, $\forall y \!\in\! \mc B$; $\alpha_{N+1} \!<\!2$, $\gamma^{\text{mg}} \!<\! \frac{1}{N}$, $\beta^{\text{tg}}\! <\! \frac{1}{|\mc N| \!+\! |\mc B|}$, $\beta_y^{\text{pb}} \!<\! \frac{1}{1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|}$,  $\forall y\!\in\! \mc B $.%

@@

\smallskip
\State 
$\psi_i(k) = 
	\col \Big(-\mu_y^{\text{pb}}(k),-\mu_y^{\text{pb}}(k),
	{
	%\left(
	\left[
	\begin{smallmatrix}
	I_H\\
	- I_H 
	\end{smallmatrix}
	\right] 
	%\otimes I_H
%\right)	
	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
	%
	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)$
\Comment{auxiliary vector}

@@

\Comm{ (to DNO and trading partners)}
\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)- p^{\text{st}}_i(k+1)$
\Comment{auxiliary vector: local load unbalance}
\State
$
p^{\textrm{mg}}_{i}(k+1), \eta_i(k+1)  \longrightarrow  \text{DNO,}
$
\Comment{forward to DNO}
     \ForAll{prosumer $ j \in \mc N_i$}

>>>>

\smallskip
We consider a linear approximation of power-flow equations, which is standard in the literature of P2P markets, e.g., \cite{yang2019,moret2020}. Specifically, for each bus $y \in \mc B$, it must hold that
\begin{equation}
\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \left(p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}\right)-p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
\end{equation}
which indicates local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption and line powers. Moreover, it must hold that
\begin{subequations}
\small
\label{eq:pf_pq}
\begin{align}
&p_{(y,z)}^{\ell} = B_{(y,z)}\left({\theta_y - \theta_z} \right) - G_{(y,z)}\left(v_y - v_z \right), \, \, \forall z \in \mc B_y, \label{eq:pf_p}\\
&q_{(y,z)}^{\ell} = G_{(y,z)}\left({\theta_y - \theta_z} \right) + B_{(y,z)}\left(v_y - v_z \right), \, \,  \forall z \in \mc B_y, \label{eq:pf_q}
\end{align}
\label{eq:pf_all}
\end{subequations}
which represent the power flow equations of line $(y,z)$ from the perspective of bus $y$, with $B_{(y,z)}$ and  $G_{(y,z)}$ denoting the susceptance and conductance, respectively, of line $(y,z)$. Note that by \eqref{eq:pf_p} and \eqref{eq:pf_q}, for each pair $(y,z) \in \mc L$, it holds that $p_{(y,z)}^{\ell} = {-p}_{(z,y)}^{\ell}$ and $q_{(y,z)}^{\ell} = {-q}_{(z,y)}^{\ell}$.

@@

\begin{remark}
Our definitions of $J_i$, $\mc U_i$ and $\mc C$ satisfy Assumption \ref{as:gen}. Moreover, these definitions can be expanded by incorporating additional cost terms, for example, related to the degradation of storage units and constraints (e.g. ramping constraints of dispatchable generation units), as long as Assumption \ref{as:gen} remains satisfied.  \marginnote{\note{R3-2}} \edit{Additionally, instead of considering linear power flow equations in \eqref{eq:pf_all}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect. II-A]{molzahn2017} can be considered since it still satisfies Assumption 1. In this case, only the definition of $\mc U_{N+1}$ differs from the current formulation.}\eod
\end{remark}

@@

\begin{algorithm*}[htbp]
\caption{Distributed P2P Markets Clearing Mechanism \red{[check modification because of extra variables of charging and discharging]}}
\label{alg:alg1}
\begin{algorithmic}[1]
\small

\init{ }
\State
\textbf{Prosumers.} For all $i \in \mc N$: set $u_i(0) \in \mc U_i$, $\mu^{\text{tr}}_{(i,j)}(0) = \0$, $\forall j \in \mc N_i$; $\alpha_i \!<\! 
\red{3} +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$.
\State
\textbf{DNO.} Set $u_{N+1}(0) \!\in\! \mc U_{N+1}$, $\lambda^{\text{mg}}\!=\!\0$, $\mu^{\text{tg}} \!=\! \0$, $\mu_y^{\text{pb}}(0)\! = \!\0$, $\forall y \!\in\! \mc B$; $\alpha_{N+1} \!<\!2$, $\gamma^{\text{mg}} \!<\! \frac{1}{N}$, $\beta^{\text{tg}}\! <\! \frac{1}{|\mc N| \!+\! |\mc B|}$, $\beta_y^{\text{pb}} \!<\! \frac{1}{1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|}$,  $\forall y\!\in\! \mc B $.%

@@

\smallskip
\State 
$\psi_i(k) = 
	\col \Big(-\mu_y^{\text{pb}}(k),-\mu_y^{\text{pb}}(k), \edit{-\mu_y^{\text{pb}}(k),}
	{
	%\left(
	\left[
	\begin{smallmatrix}
	I_H\\
	- I_H 
	\end{smallmatrix}
	\right] 
	%\otimes I_H
%\right)	
	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
	%
	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)$
\Comment{auxiliary vector}

@@

\Comm{ (to DNO and trading partners)}
\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)\edit{- p^{\text{ds}}_i(k+1)+p^{\text{ch}}_i(k+1)}$
\Comment{auxiliary vector: local load unbalance}
\State
$
p^{\textrm{mg}}_{i}(k+1), \eta_i(k+1)  \longrightarrow  \text{DNO,}
$
\Comment{forward to DNO}
     \ForAll{prosumer $ j \in \mc N_i$}
